Fail Faster

### 2025-03-22 paper/paper.tex
intro of s3

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \hg{TODO: Abstract}
\end{abstract}

@@

%\jwc{``Property based testing is a race against time...''}
Property-based testing (PBT) is a software testing technique that uses
random test inputs to validate logical specifications. Recent studies on PBT usage~\cite{inpractice} in industry have shown that
practitioners often interleave PBT with their software development process, sometimes
testing their properties every time they save their code. This means that PBT is often given a very short time
window to find bugs---e.g., between 50 milliseconds and 30 seconds~\cite{inpractice}.
The faster a test fails, the better.
% The goal of PBT is to fail tests as fast as possible. \jwc{First cut at ``fail fast''}
\iflater 
\bcp{Feels like we're missing a trick in the transition here.  Can we
  say, ``Because performance is important, PBT libraries are already
  quite tuned.  [Can we substantiate that??]  But more is
  possible...'' }
\fi

@@

With a sense of the inefficiences pervasive in generator libraries, we set out in this section to find solutions.
\todo{JWC}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \hg{TODO: Abstract}
  \jwc{Make sure we are clear about our results here. I.e. VERY QUICKLY in this abstract, we need to say ``finds bugs 5x faster''}
\end{abstract}

@@

%\jwc{``Property based testing is a race against time...''}
Property-based testing (PBT) is a software testing technique that uses
random test inputs to validate logical specifications. Recent studies on PBT usage in industry~\cite{inpractice} have shown that
practitioners often interleave PBT with their software development process, sometimes
testing their properties every time they save their code. This means that PBT is often given a very short time
window to find bugs---e.g., between 50 milliseconds and 30 seconds~\cite{inpractice}.
The faster a test fails, the better.
% The goal of PBT is to fail tests as fast as possible. \jwc{First cut at ``fail fast''}
\iflater 
\bcp{Feels like we're missing a trick in the transition here.  Can we
  say, ``Because performance is important, PBT libraries are already
  quite tuned.  [Can we substantiate that??]  But more is
  possible...'' }
\fi

@@

With a sense of the inefficiences pervasive in generator libraries, we set out in this section to investigate solutions.
We begin with a quick tour through multi-stage programming, and then incrementally build \camlname, layering on features and functionality.
Last, we present the controlled experiment we use to demonstrate how faster \rand{} leads to failing faster.
